Language-Based Security for Low-Level MPC

### 2024-05-22 ppdp24/intro.tex
spelling

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. The security semantics of
MPC include both confidentiality and integrity properties incorporated
into models such as real/ideal (aka simulator) security and universal
composability (UC), developed primarily by the cryptography community
\cite{evans2018pragmatic}.  Related proof methods are well-studied
\cite{Lindell2017} but mostly manual. Somewhat independently, a
significant body of work in programming languages has focused on
definition and enforcement of confidentiality and integrity
\emph{hyperproperties} \cite{10.5555/1891823.1891830} such as
noninterference and gradual release
\cite{4223226,sabelfeld2009declassification}. Following a tradition of
connecting cryptographic and PL-based security models
\cite{10.1007/3-540-44929-9_1,10.1145/3571740}, recent work has also
recognized connections between MPC security models and hyperpoperties
of, e.g., noninterference \cite{8429300}, and even leveraged these
connections to enforce MPC security through mechanisms such as
security types \cite{10.1145/3453483.3454074}. Major benefits of this
connection in an MPC setting include better language abstractions for
defining protocols and for mechanization and even automation of
security proofs.  The goal of this paper is to develop a PL model for
defining a variety of low-level probabilistic MPC protocols, to
formulate a collection of confidentiality and integrity
hyperproperties for our model model with familiar information flow
analogs, and to show how these properties can be leveraged for
improved proof automation.

@@

\paragraph{Fully and partially automated verification.} In Section
\ref{section-bruteforce} we develop a method for automatically
computing the pmf of $\minifed$ protocols in $\mathbb{F}_2$, that can
be automatically queried to enforce hyperperproperties of
security. This method is perfectly accurate but has high complexity;
we show this can be partially mitigated by conversion of protocols in
$\mathbb{F}_2$ to stratified Datalog which is amenable to HPC
acceleration. Furthermore, in Section \ref{section-example-gmw} we
consider in detail how this automated technique can be used as a local
automated tactic for proving security in arbitrarily large GMW
circuits using conditional probabilistic independence as in
\cite{li2023lilac} (Lemmas \ref{lemma-gmwtactic} and \ref{lemma-gmwinvariant}
and Theorem \ref{theorem-gmw}).

>>>>

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. The security semantics of
MPC include both confidentiality and integrity properties incorporated
into models such as real/ideal (aka simulator) security and universal
composability (UC), developed primarily by the cryptography community
\cite{evans2018pragmatic}.  Related proof methods are well-studied
\cite{Lindell2017} but mostly manual. Somewhat independently, a
significant body of work in programming languages has focused on
definition and enforcement of confidentiality and integrity
\emph{hyperproperties} \cite{10.5555/1891823.1891830} such as
noninterference and gradual release
\cite{4223226,sabelfeld2009declassification}. Following a tradition of
connecting cryptographic and PL-based security models
\cite{10.1007/3-540-44929-9_1,10.1145/3571740}, recent work has also
recognized connections between MPC security models and hyperproperties
of, e.g., noninterference \cite{8429300}, and even leveraged these
connections to enforce MPC security through mechanisms such as
security types \cite{10.1145/3453483.3454074}. Major benefits of this
connection in an MPC setting include better language abstractions for
defining protocols and for mechanization and even automation of
security proofs.  The goal of this paper is to develop a PL model for
defining a variety of low-level probabilistic MPC protocols, to
formulate a collection of confidentiality and integrity
hyperproperties for our model model with familiar information flow
analogs, and to show how these properties can be leveraged for
improved proof automation.

@@

\paragraph{Fully and partially automated verification.} In Section
\ref{section-bruteforce} we develop a method for automatically
computing the pmf of $\minifed$ protocols in $\mathbb{F}_2$, that can
be automatically queried to enforce hyperproperties of
security. This method is perfectly accurate but has high complexity;
we show this can be partially mitigated by conversion of protocols in
$\mathbb{F}_2$ to stratified Datalog which is amenable to HPC
acceleration. Furthermore, in Section \ref{section-example-gmw} we
consider in detail how this automated technique can be used as a local
automated tactic for proving security in arbitrarily large GMW
circuits using conditional probabilistic independence as in
\cite{li2023lilac} (Lemmas \ref{lemma-gmwtactic} and \ref{lemma-gmwinvariant}
and Theorem \ref{theorem-gmw}).
